%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Jesus A.} % Your first name
\familyname{Rodriguez Perez} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{Flat 3/2, 41 Braeside Street}{Glasgow, Lanarkshire}
\mobile{07516881104}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{rpsoft@gmail.com}
\homepage{http://www.dcs.gla.ac.uk/~jesus/}{dcs.gla.ac.uk/~jesus} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{Data Specialist and PhD on Information Retrieval}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-2] % Dummy text
%\lipsum[4] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}
\cventry{2021--present}{Data Science Lecturer}{}{School of Computing Science}{University of Glasgow, UK}{Teaching data science courses and supervising of projects involving NLP, Machine Learning, Information Retrieval and related technologies.
	\vspace{0.25cm}
	\begin{itemize}
		\item \textbf{Text As Data} Course. This course delivers an introduction to leveraging text as a source of data. Students are taught about language models, text classification (machine learning), NLP, embeddings, and modern contextual language models based on transformer architectures.
		\item \textbf{Introduction to Data Science and Systems} Course. My section deals with database systems. Particularly, how is data physically organised, how data structures facilitate querying, as well as techniques to estimate query execution costs which enable query optimisation.
	\end{itemize}
	\vspace{0.25cm}
}

\cventry{2017--2020}{Research Associate}{}{Institute of Health \& Wellbeing}{University of Glasgow, UK}{Assisting on research about diabetes and cardiovascular issues, eligibility criteria to medical trials and streamlining the research processes within the institute.
\vspace{0.25cm}
\begin{itemize}
	\item Developed \textbf{TableTidier}, tool that utilises informed classifiers for the semi-automated extraction of data from PDF tables preserving relationships with headings. \\(Demo: \url{https://vimeo.com/365161796})
	\item Created \textbf{R for Researchers} an online course for the University of Glasgow, which aims to introduce R tools to streamline research activities within the Health and Wellbeing Institute. Focused on version control and publication libraries. (Course link: \url{https://youtube.com/watch?v=f5W3cNbfT2w})
\end{itemize}
\vspace{0.25cm}
}

\cventry{2015--2017}{Data Specialist}{}{CREATe - School of Law}{University of Glasgow, UK}{Provide data-driven solutions to copyright research problems, maintain IT infrastructures and design \& develop software. Involved in numerous projects:
\vspace{0.25cm}
\begin{itemize}
\item \textbf{Online Media Behaviour Analytics.} A web tool to allow the interrogation and data extraction from Ofcom/IPO survey datasets on infringement and media consumption behaviour in the UK. (\url{http://www.create.ac.uk/omeba})
\item \textbf{Intellectual Property - Oral History Project.} A web registry of IP related material. Developed the site from the ground up using NodeJS, React and other state-of-the-art web technologies. (\url{http://iporalhistory.co.uk})
\item \textbf{Digitising the Edwin Morgan Scrapbooks.} Portal and annotation tool development. (\url{www.digitisingmorgan.org})
\item \textbf{Litigation Explorer.} Web tool to interrogate a dataset of IP litigation cases from the small claims court in London. (\url{http://copyrightcentral.arts.gla.ac.uk/litexp})
\item \textbf{Creative Output in a Market Context}. Real-time and multi-user evaluation platform to study the effects of creativity in a economics context.
%\item \textbf{IPWatchr - Demo.} Monitoring of social media profiles sharing infringing content connected with the product's P2P activity. (http://copyrightcentral.arts.gla.ac.uk/ipwatchr)
\item \textbf{EU Hackathon. } Co-organiser of the challenges for the copyright-related 2016 EU Hackathon. (\url{http://2016.euhackathon.eu/})
\end{itemize}
\vspace{0.25cm}
}

%------------------------------------------------

\cventry{2015}{Search Engine Specialist}{}{Scoop Analytics}{UK}{Built the initial search engine to provide ad-hoc search access to real-time tweets utilising a retrieval approach based on my thesis.}

%------------------------------------------------

%\subsection{Miscellaneous}

\cventry{2011--2015}{University Tutor}{Computing School}{University of Glasgow}{UK}{Supervised multiple student groups. Evaluated and provided students with personalised help on their practical assessments}

\cventry{2009--2015}{Library Demonstrator}{Computing Help Desk}{University of Glasgow}{UK}{Ensured the smooth running of the library computing services and providing students with technical assistance.}

\cventry{2008}{Software Developer}{School of Psychology}{University of Glasgow}{UK}{Software development and data processing assistance on brain imaging data for a MoD-sponsored project supervised by Prof. Frank Pollick}



%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Collaborations}
\begin{itemize}
	\item \textbf{Ten Assumptions About Artificial Intelligence That Can Mislead Patent Law Analysis} Research paper examines a set of assumptions about artificial intelligence, often taken as factual premises in discussions regarding ‘artificial ingenuity’ -  2021\\ (\url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3910332})
	\item \textbf{How Much Do Consumers Value Interoperability?} Research paper utilising web scrapped data on sales and reviews of DVD players to study the effects of DRM. - 2017\\ (\url{https://papers.ssrn.com/sol3/papers.cfm?abstract\_id=2998767})
\end{itemize}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\label{firstPage}
%\section{PhD Thesis}
%Specialised on microblog retrieval ad-hoc search and retrieval models.
\cventry{2011--2017}{PhD in Information Retrieval}{}{University of Glasgow}{UK}{}
\subsection{Thesis Details}
\cvitem{Title}{\emph{Microblog Retrieval. Challenges and Opportunities}}
\cvitem{Supervisor}{Professor Joemon M. Jose}
\cvitem{Description}{Explores the problems faced by the state-of-the-art retrieval models when utilised under microblog ad-hoc retrieval conditions. A number of retrieval techniques were developed to improve ad-hoc retrieval performance of microblogs covering information retrieval areas such as: \textit{retrieval models}, \textit{automatic query expansion}, and \textit{query performance prediction}.}
\subsection{Publications}
\cvitem{}{
	\begin{itemize}
		%\item Jesus A. Rodriguez Perez, and Joemon M. Jose. ``MBRM: A Microblog Retrieval Model'' TOIS 2018. (Under Review).
		\item Jesus A. Rodriguez Perez, and Joemon M. Jose. ``On Microblog Dimensionality and Informativeness'' Proceedings of ICTIR 2015.
		\item Jesus A. Rodriguez Perez, and Joemon M. Jose. ``Predicting Query Performance in Microblog Retrieval'' Proceedings of the 37th ACM SIGIR conference. 2014.
		\item Jesus A. Rodriguez Perez, et al. ``On using inter-document relations in microblog retrieval.'' Proceedings of the 22nd international conference WWW 2013.
	\end{itemize}
}

\cventry{2006--2011}{Bsc in Computing Science}{}{University of Glasgow}{UK}{}
\cvitem{}{Dissertation on collaborative search. Published as \textit{CoFox: a visual collaborative browser} in CIKM2011 (http://www.cikm2011.org/)}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}
%\subsection{}
\cventry{2014}{First Prize (\pounds20000) at Future Cities Hackathon 2014}{}{Glasgow}{}{Web tool to assess road quality, traffic and other road events. (Team of 5)}

\cventry{2013}{First and \textit{``people's choice''} prizes at Amazon Hackathon 2013}{}{Edinburgh}{}{Web application to map drug usage across the country from a NHS dataset. (Team of 3)}


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}
\cvitem{Web development}{NodeJS, ReactJS, ExpressJS, MaterialUI, PHP, JQuery, SQL, XQuery, HTML5, CSS}
\cvitem{Technologies}{Hadoop, Machine Learning(SKlearn \& Weka), Lucene, WordNet, Unity }
\cvitem{Operating Systems}{Advanced user of Debian-based distributions, Advanced Windows User}
\cvitem{Games Development}{Unity with C\# (Android)}


%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{Communication Skills}
%
%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitem{Spanish}{Mothertongue}{}
\cvitem{English}{Fluent}{}
\cvitem{French}{Basic Command}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Composing Music}{Guitar \& Bass}
\cvlistdoubleitem{Gaming}{Games development}
\cvlistdoubleitem{Climbing}{Football}
\cvlistdoubleitem{Martial Arts}{Cooking}

%----------------------------------------------------------------------------------------

\end{document}